---
title: "hw5 jw4007"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(patchwork)

library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### q2
#### import data
```{r}
homicide_csv = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide = read.csv(homicide_csv)
```

#### create the "city_state" variable and summarize within cities to obtain the total number of homicides and the number of unsolved homicides
```{r}
homicide = homicide %>%
  mutate(city_state = str_c(city, state, sep = ","))

describe = homicide %>%
  group_by(city) %>%
  summarize(total_cases = n(),
            total_unsolved = sum(disposition == c("Closed without arrest", "Open/No arrest")))

knitr::kable(describe)
```
After creating the "city_state" variable, there are `r nrow(homicide)` observations and `r ncol(homicide)` variables in the dataset. The variables are `r names(homicide)`. 
The above table summarizes the total number of homicide cases and the number of unsolved homicides for the 50 large U.S. cities.

```{r}
describe_baltimore =
  describe %>%
  filter(city == "Baltimore") 

baltimore_test = prop.test(
  x = pull(describe_baltimore, total_unsolved),
  n = pull(describe_baltimore, total_cases)) %>%
  broom::tidy() %>%
  select(estimate, conf.low, conf.high)

knitr::kable(baltimore_test)
```
The above table describes the estimate the proportion of homicides that are unsolved and its confidence intervals from the city of Baltimore, MD.

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.
```{r}
city_prop_test_fun = function(city_df) {
  
  city_summary = city_df %>%
  summarize(total_cases = n(),
            total_unsolved = sum(disposition == c("Closed without arrest", "Open/No arrest")))
  
  test = 
    prop.test(
    x = pull(city_summary, total_unsolved),
    n = pull(city_summary, total_cases)) %>%
    broom::tidy() %>%
    select(estimate, conf.low, conf.high)
  
  test
}

city_results =
  homicide %>%
  nest(data = uid:disposition) %>%
  mutate(results = map(data, city_prop_test_fun)) %>%
  select(city_state, results) %>%
  unnest(results)

```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.
```{r}
city_results %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) + geom_bar() + geom_errorbar(aes(ymin = conf.low, ymax = conf.high))
``` 


```{r}
```

